Have you forgotten?' Conversion experiences in shopping lists

### 2017-02-07 lists_conversion_experience.rmd
some local changes?

---
title: "'Have you forgotten?' Conversion experiences in shopping lists"
author: "Adrian Mackenzie"
date: "`r Sys.Date()`"
output:
tufte::tufte_handout: default
citation_package: biber
latex_engine: xelatex
bibliography: /home/mackenza/ref_bibs/uni.bib
link-citations: yes
header-includes:
    - \usepackage{setspace}
    - \doublespacing
---

# 'Have you forgotten?' Conversion experiences in shopping lists

@@

## Abstract

@@

## Introduction: the presentation of a presentation

@@

```{r random_basket, echo=FAlSE, cache=TRUE, fig.cap='Random basket'}
library(dplyr)
library(ggplot2)
library(readr)
library(knitr)
csvs = list.files('data', pattern = '*.csv',full.names=TRUE)
df = bind_rows(sapply(csvs, read_tsv))
kable(sample_n(df, size=5)$name, col.names='item')
```

@@

## How do we approach lists as objects of research?

@@

## 1. The context of the presentation: 'statistics and operations research in industry'

@@

## 2. The web and the shopping basket: how it was reconstituted in the 1990s

@@

## 3. The rules-based list and the `apriori` algorithm

@@

```{r arules, cache=TRUE, echo=FALSE, fig.margin=TRUE}
library(knitr)
library(arules)
library(arulesViz)
library(datasets)
data(Groceries)
itemFrequencyPlot(Groceries,topN=10,col=rainbow(10), ntype="absolute",  cex.axis = 0.55)
options(digits=2)
rules<-apriori(data=Groceries, parameter=list(supp=0.001,conf = 0.15,minlen=2), appearance = list(default="rhs",lhs="whole milk"), control = list(verbose=F))
rules<-sort(rules, decreasing=TRUE,by="confidence")
inspect(rules[1:5]) 
items = Groceries@itemInfo
```

The association rule-based model for the `Groceries` dataset suggests some of the characteristic ordering practices of 1990s-style data-mining approaches to lists. 
The association between items is expressed in the form of _rules_. These rules, a term derived from decision support literature, define sets of associations between items. As a set theory-based practice, the association rules define likely sets of items or shopping baskets in terms of decreasing probability.   `r inspect(rules[1])` is a stronger association than `r inspect(rules[2])`. So any recommendation in the 'Have You Forgotten' list should probably put them in that order.

@@

## 4. Hack? Customers go straight to the checkout

@@

## 5. 'We have 52 weeks of data for each customer': how is order constructed -- from history?

@@

## 6. Gain: use good features to build models

@@

## 7. Sparsity: output 20 recommendations from 200,000 products

@@

## 8. Value: Balancing conversion vs spend
The value of an ordering

## 9. Metric: precision-at-K

@@

## 10. Experimental settings: A/B allocation and uplift

@@

## 11. Infrastructure: realtime engine serves up top 5

@@

## 12. Similarity, substitution, complementarity and micrological propensities

@@

## 13. Complementarity drives conversion

@@

## Conclusion

@@

## References

>>>>

---
title: "'Have you forgotten?' Conversion experiences in shopping lists"
author: "Adrian Mackenzie"
date: "`r Sys.Date()`"
output:
tint::tintPdf: default
citation_package: biber
latex_engine: xelatex
bibliography: /home/mackenza/ref_bibs/uni.bib
link-citations: yes
header-includes:
    - \usepackage{setspace}
    - \doublespacing
---

@@

# Abstract

@@

# Introduction: the presentation of a presentation

@@

```{r random_basket, echo=FALSE, cache=TRUE, fig.cap='Random basket', fig.margin=TRUE}
library(dplyr)
library(readr)
library(knitr)
csvs = list.files('data', pattern = '*.csv',full.names=TRUE)
df = bind_rows(sapply(csvs, read_tsv))
kable(sample_n(df, size=5)$name, col.names='Items')
```

@@

# How do we approach lists as objects of research?

@@

# 1. The context of the presentation: 'statistics and operations research in industry'

@@

# 2. The web and the shopping basket: how it was reconstituted in the 1990s

@@

# 3. The rules-based list and the `apriori` algorithm

@@

```{r arules, cache=TRUE, echo=FALSE, fig.margin=TRUE}
library(knitr)
library(arules)
library(arulesViz)
library(datasets)
data(Groceries)
itemFrequencyPlot(Groceries,topN=10,col=rainbow(10), ntype="absolute",  cex.axis = 0.55)
options(digits=2)
rules<-apriori(data=Groceries, parameter=list(supp=0.001,conf = 0.15,minlen=2), appearance = list(default="rhs",lhs="whole milk"), control = list(verbose=F))
rules<-sort(rules, decreasing=TRUE,by="confidence")
inspect(rules[1:5]) 
rule2 = inspect(rules[2])
rule1 = inspect(rules[1])
items = Groceries@itemInfo
```

The association rule-based model for the `Groceries` dataset suggests some of the characteristic ordering practices of 1990s-style data-mining approaches to lists. 
The association between items is expressed in the form of _rules_. These rules, a term derived from decision support literature, define sets of associations between items. As a set theory-based practice, the association rules define likely sets of items or shopping baskets in terms of decreasing probability.   `r rule1` is a stronger association than `r rule2`. So any recommendation in the 'Have You Forgotten' list should probably put them in that order.

@@

# 4. Hack? Customers go straight to the checkout

@@

# 5. 'We have 52 weeks of data for each customer': how is order constructed -- from history?

@@

# 6. Gain: use good features to build models

@@

# 7. Sparsity: output 20 recommendations from 200,000 products

@@

# 9. Metric: precision-at-K

@@

# 10. Experimental settings: A/B allocation and uplift

@@

# 11. Infrastructure: realtime engine serves up top 5

@@

# 12. Similarity, substitution, complementarity and micrological propensities

@@

# 13. Complementarity drives conversion

@@

# Conclusion

@@

# References
